**Title:** Analyzing long-term water quality of lakes in Rhode Island and the Northeastern United States with an anomaly approach

### 2020-12-04 manuscript/ecosphere_resubmit_2/ecosphere_response_2.Rmd
text revisions complete.  Now on to figure/tables.
draft of all SME revisions completed.

*Response:* NEEDS RESPONSE

@@

*Response:* NEEDS RESPONSE

@@

*Response:* Thanks!  After about 100 failed attempts at trying to describe this approach, we finally decided to put this together.  Actually caught some initial errors in code with this!

@@

*Response:* NEEDS RESPONSE

@@

*Response:* NEEDS RESPONSE

@@

*Response:* NEEDS RESPONSE

@@

*Response:* NEEDS RESPONSE

>>>>

*Response:* Good point.  We added an additional paragraph to the Introduction addressing RI LULC and pressures.

@@

*Response:* Good suggestion.  I never liked these tables, but figured readers would want details on variation (or lack thereof) in sampling effort. Created a faceted plot for each lagosne and uriww to replace the tables.

@@

*Response:* Thanks!  After about 100 failed attempts at trying to describe this approach to colleagues, we finally decided to put this together.  Actually caught some initial errors in code with this!

@@

*Response:* Added description of regression line to caoptions and increased title text size.

@@

*Response:* Have moved plots closer together

@@

*Response:* Done.

@@

*Response:* Good catch.  The original language was confusing.  Caption now reads: "Panel A. Simulated, random data showing example of three hypothetical lakes; one lake was monitored throughout the record, one lake with low reported values monitored early in the record, and another lake with high reported values monitored late in the record.  Panel B. Analysis of simulated, random data with one lake monitored throughout the record, one lake with low reported values monitored early in the record, and another lake with high reported values monitored late in the record. Yearly average of the actual values is shown in red and yearly average of the site-specific anomalies is shown in blue."  Plus, have indicated in the methods (third paragaraph of Study Area and Data) that "lakes and reservoirs" are referred to as "sites" throughout the paper.
